>

### 2025-01-31 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
anonymize pre-regs & rmd

author-information: > 
    \author{{\large \bf Veronica Boyce (vboyce@stanford.edu)} \\ Department of Psychology, \\Stanford University \And {\large \bf Robert Z. Sparks (bsparks@stanford.edu) }\\ Department of Psychology, \\Stanford University
    \AND {\large \bf Yannick Mofor (yannickm@stanford.edu)} \\ Department of Computer Science, \\ Stanford University \And {\large \bf Michael C. Frank (mcfrank@stanford.edu)} \\ Department of Psychology, \\ Stanford University}

@@

Our goal for Experiment 1 was to test young children's ability to coordinate on descriptions of abstract shapes that their partner could understand. Young children can be very sensitive to task demands and cognitive load [@turan-kucuk2024; @keen2003; @carruthers2013], so we adapted the experimental framework from @leung2024, and further simplified it by reducing the total pool of targets and the number of trials. This experiment was pre-registered at https://osf.io/kcv8j.

@@

As Experiment 2 was very similar to Experiment 1, we focus on the changes made compared to Experiment 1. Experiment 2 was pre-registered at https://osf.io/y2dax.

>>>>

author-information: > 
    \author{Anonymized}

@@

Our goal for Experiment 1 was to test young children's ability to coordinate on descriptions of abstract shapes that their partner could understand. Young children can be very sensitive to task demands and cognitive load [@turan-kucuk2024; @keen2003; @carruthers2013], so we adapted the experimental framework from @leung2024, and further simplified it by reducing the total pool of targets and the number of trials. This experiment was pre-registered at https://osf.io/kcv8j?view_only=fd55733671194962b868a4ba19377631.

@@

As Experiment 2 was very similar to Experiment 1, we focus on the changes made compared to Experiment 1. Experiment 2 was pre-registered at https://osf.io/y2dax/?view_only=fd55733671194962b868a4ba19377631.
